### 2017-01-25 R/ITHIM.Rmd
Created NHTS sample size figure

>>>>

```{r sampleSize, eval = TRUE, dev=c('pdf', 'png'), fig.width = 3*fig.width, fig.asp = 1/phi, echo = TRUE, warning = FALSE}
foo <- lapply( countMatrix, function(x) c(x) )
foo <- melt(foo)
names(foo) <- c("sampleSize", "state")
p <- ggplot(foo, aes( x = state, y = sampleSize))
p + geom_bar(stat = "identity") + scale_y_log10() + labs(y = "Sample Size (Referent Group)", x = "State") + theme_bw()
```
